Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
cool
Update on Overleaf.

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. 
Inner product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer product computes the product of all pairs of elements from the input matrices.
More detailed explanation is available in Section 2.2 of ~\cite{zhang2021gamma}.
Figures ~\ref{spgemm_small} and ~\reef{spgemm_large} show

>>>>

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner-product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. 
Inner-product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer-product computes the product of all pairs of elements from the input matrices.
More detailed explanation is available in Section 2.2 of ~\cite{zhang2021gamma}.
Figures ~\ref{spgemm_small} and ~\reef{spgemm_large} show SpGEMM results with Finch and TACO.
Note that inner-product is pretty ineffi
